# Sentiment analysis for UK 2019 general election candidates

In this task, you will get a sample of Tweets mentioning the two leading party candidates for the UK election (scheduled for December 12, 2019): Boris Johnson and Jeremy Corbyn.

## Getting the data

Use the **rtweet** package to get two samples of Tweets:
-  a set for Boris Johnson, and
-  a set for Jeremy Corbyn.
```{r}
install.packages("rtweet")
library("rtweet")

JC <- "Jeremy Corbyn"
BJ <- "Boris Johnson"

jc_tweets <- search_tweets(
  JC, n = 1000, include_rts = FALSE
)

bj_tweets <- search_tweets(
  BJ, n = 1000, include_rts = FALSE
)

labour_tweets <- search_tweets(
  "Labour", n = 1000, include_rts = FALSE
)

conservative_tweets <- search_tweets(
  "Conservative", n = 1000, include_rts = FALSE
)

origin <- c(rep("Corbyn", 1000), 
            rep("Boris", 1000), 
            rep("Labour", 1000),
            rep("Conservative", 1000))

# Some names can be for other people
data = rbind(jc_tweets, bj_tweets, labour_tweets, conservative_tweets)
data$origin <- origin
```


You can refer to the (updated) example from Week 7's REST example, using the `search_tweets()` function.  Get as large a sample as you can, with equal numbers for both sides.  Consider your search patterns carefully!

## Comparing sentiment

Use the **quanteda** package to analyze the sentiment for the tweets.  This will involve:

- converting the tweet objects to a quanteda corpus (this works with `corpus()`)

- adding a new document variable called `candidate` to each corpus (there should be two), using the `docvars(corpus1, "candidate") <- "corbyn"` (for instance)

- adding the two corpora together, see `?`.corpus``.

- creating a dfm using the built-in `data_dictionary_LSD2015`.  See `?dfm` and the `dictionary` argument.  To group the documents, consider the `groups` argument for the new `candidate` document variable.

```{r}
library(quanteda)
corp_jc <- corpus(jc_tweets)
summary(corp_jc)

corp_bj <- corpus(bj_tweets)

# add doc variable
docvars(corp_jc, "candidate") <- "corbyn"
docvars(corp_bj, "candidate") <- "boris"

# Add them toguether
corpus_data <- corp_bj + corp_jc

# Create a DFM
dfm <- dfm(x = corpus_data, 
           dictionary = data_dictionary_LSD2015, 
           groups = "candidate")

dfm

dfm_mat <- data.frame(matrix(dfm@x, nrow = 2, dimnames = dfm@Dimnames))
dfm_mat$candidate <- dfm@Dimnames[[1]]
dfm_mat
```

# Interpret the results

Here you can compare the positive to negative words for each candidate, possibly using a plot.

```{r}
library(tidyverse)
dta_long <- pivot_longer(dfm_mat,cols = c("negative", "positive",
                              "neg_positive","neg_negative")
             , names_to = "Sentiment")

ggplot(data = dta_long, aes(x = candidate, y = value, colour = Sentiment)) +
  geom_point(size)

dta_long

ggplot(data = dta_long, aes(x = Sentiment, y = value, fill = candidate)) +
  geom_bar(stat = 'identity', position = 'dodge')
```

